Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-13 Paper/gammaRays.tex
Correction to Burst Data Download

For background estimation, we also download observational data during a day before the burst.
All the values are put the same into the form, except the time range:
\begin{align*}
	\texttt{time} + \texttt{startOffset} &- 0.5\left(\texttt{endOffset} - \texttt{startOffset}\right) - 86400,\\
	\texttt{time} + \texttt{startOffset} &- 0.5\left(\texttt{endOffset} - \texttt{startOffset}\right)
\end{align*}

@@

The second one is \texttt{gtmktime}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtmktime.txt}}. It uses the spacecraft file as well as events file, and filters out time periods when Fermi LAT was not operational. Running \texttt{gtmktime} is also required for exposure maps calculation, which we'll need later on. Parameters are the following\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/data_preparation.html}}:
\begin{lstlisting}
gtmktime scfile=[spacecraft] sctable=SC_DATA
	filter="DATA_QUAL>0 && LAT_CONFIG==1" roicut=yes
	evfile=filtered.fits evtable=EVENTS outfile=timed.fits
	apply_fiter=yes
\end{lstlisting}
where \texttt{[spacecraft]} is the FITS containing the spacecraft data.

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky. Before using the data obtained from it, we should perform a more elaborate filtering by location using Fermi LAT's point spread function. The procedure is described in the following section.

>>>>

For background estimation, we also download observational data during a day before the burst.
All the values are put the same into the form, except for the time range:
\begin{align*}
	\texttt{time} + \texttt{startOffset} &- 0.5\left(\texttt{endOffset} - \texttt{startOffset}\right) - 86400,\\
	\texttt{time} + \texttt{startOffset} &- 0.5\left(\texttt{endOffset} - \texttt{startOffset}\right)
\end{align*}

@@

The second one is \texttt{gtmktime}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtmktime.txt}}. It uses the spacecraft file as well as events file, and filters out time periods when Fermi LAT was not operational. Running \texttt{gtmktime} is also required for exposure maps calculation, which we'll need later on. Parameters are the following\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/data_preparation.html}}:
\begin{lstlisting}
gtmktime scfile=[spacecraft] sctable=SC_DATA
	filter="DATA_QUAL>0 && LAT_CONFIG==1" roicut=yes
	evfile=filtered.fits evtable=EVENTS outfile=timed.fits
	apply_fiter=yes
\end{lstlisting}
where \texttt{[spacecraft]} is the FITS file containing the spacecraft data.

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky. Before using the data obtained from it, we should perform a more elaborate filtering by location using the point spread function of Fermi LAT. The procedure is described in the following section.
